DRAFT: Harmonized and trait aggregation paper

### 2020-10-16 Paper/Results/Results_trait_harmonization.tex
05.09.2020: Minor edits SI
16.10: Paper Update, first implm. of Co-Authors

\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features}

Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI). According to the RDA of the trait composition sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species. Only species with the trait life cycle duration $> 1$ year fail to characterize sites with high salinization. Also, life cycle duration $<= 1$ year is not anymore characterizing sites not impacted by salinity. Like in the original analysis, transition and upstream sites from the point source are characterized by univoltine species and species that lay their eggs in an aquatic environment. We constructed also the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found results similar to the original analysis (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).

For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}). Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features.

% Mention that threshold according to mahalanobis distance is almost reached for life cycle duration

@@

>>>>

\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}

Overall, using the harmonized grouping features led to only slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI). According to the RDA of the trait composition, sites with high salinity were characterized by families that possess the traits multivoltinism, ovoviviparity, gill-respiration, and feeding mode shredder. Only families with the trait life cycle duration $> 1$ year failed to characterize sites with high salinization. Also, life cycle duration $<= 1$ year did not characterise sites not impacted by salinity. Like in the original analysis, transition and upstream sites from the point source were characterised by univoltine taxa and taxa that lay their eggs in aquatic environments. We also constructed the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found results similar to the original analyses (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).

For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}). 
% Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features. 
%? Mention that threshold according to mahalanobis distance is almost reached for life cycle duration

@@

% PUP comment: 
% What are exactly „RDA species scores“? The coordinates of species along the first factorial axis in RDA?
% If „yes“, I’m not sure this result presentation is suitable. In fact the box-plots summarizing the distributions of the set of species in the RDA analysis, after applying different strategies of trait description, can be very similar (it’s not surprising, because in each case the mean coordinate of species is 0), but the individual locations of species along each axis can be very different from an RDA to another axis (i.e. from a grouping feature definition strategy to another). It would be probably far more interesting to represent the distribution of deviations between the RDA scores provided by each strategy and the original RDA scores (from Szöcs et al., 2018)..

### 2020-10-16 Paper/Results/SI.tex
16.10: Paper Update, first implm. of Co-Authors

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
    \caption{RDA of traits constrained by electric conductivity using harmonized grouping features. Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the left indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al. \cite{szocs_effects_2014}.
    } 
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
    \caption{RDA of traits constrained by electric conductivity. Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the left indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled.
    } 
\end{figure}

\subsubsection*{Trait distribution along first RDA axis} 
\begin{figure}[H]
    \centering
    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
    \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
    } 
\end{figure}

@@

    \begin{longtable}{m{1.7cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}}

@@

        Trait & Freshwaterecology & Tachet & \specialcell{North America \\ (Twardochleb)} & 

@@

        "More than \textit{three} generations per year" \textsuperscript{\textit{b}}& 

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
    \caption{RDA of traits constrained by electric conductivity using harmonized grouping features. Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the right indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al. \cite{szocs_effects_2014}.
    } 
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
    \caption{RDA of traits constrained by electric conductivity. Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the right indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled.
    } 
\end{figure}

\subsubsection*{Trait distribution along first RDA axis}

% ASK: 
% - there seems to be some overlap of text on the top left
% - Why mention life cylce duration separately?
\begin{figure}[H]
    \centering
    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
    \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
    } 
\end{figure}

@@

    \begin{longtable}{m{1.8cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}}

@@

        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb)} & 

@@

        "\textit{Three} or more generations per year" \textsuperscript{\textit{b}}& 

### 2020-10-16 Paper/Results/Taxonomic_cov_and_info_compl.tex
16.10: Paper Update, first implm. of Co-Authors

Regarding the taxonomical coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}). By contrast, the largest taxon pool is spanned by the European trait dataset with 4110 taxa followed by the North American trait dataset that contained trait information on 3753 taxa. The Australian dataset contains 1402 taxa. The European, New Zealand, and North American datasets have most taxa on the highest taxonomical resolution while the Australian dataset has a similar number of taxa on species and genus-level.

\begin{table}[ht]
    \centering
    \caption{Number of taxa per harmonized database and per taxonomic level. Numbers in parenthesis show relative frequencies in percentage.}
    \label{tab:tax_coverage}
    \begin{tabular}{lccccc}
    \toprule[.1em]
    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic taxa \\ 
    \toprule[.1em]
    EU & 4110 & 3848 (93.63) & 237 (5.77) & 25 (0.61) & 3579 (87.08) \\ 
    NOA & 3753 & 2414 (64.32) & 1163 (30.99) & 176 (4.69) & 3305 (88.06) \\ 
    AUS & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1016 (72.47) \\ 
    NZ & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
    \bottomrule
    \end{tabular}
\end{table}

@@

The amount of entries with available information for the selected grouping features varied strongly for the European, North American, and Australian datasets (Table \ref{tab:trait_coverage}). By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).

\begin{table}[ht]
    \centering
    \caption{Displayed is the percentage of entries that have information for the individual grouping features per dataset.} 
    \label{tab:trait_coverage}
    \begin{tabular}{llllllll}
    \toprule[.1em]
    Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
    \toprule[.1em]
    EU & 7 & 16 & 24 & 33 & 11 & 56 & 65 \\ 
    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
    AUS & 5 & 48 & 51 & 42 & 78 & 70 & 99 \\ 
    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
    \bottomrule
    \end{tabular}
    \end{table}

>>>>

Regarding the taxonomical coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}). By contrast, the largest taxon pool is spanned by the European trait dataset with 4496 taxa followed by the North American trait dataset that contained trait information on 3753 taxa. The Australian dataset contains 1402 taxa. The European, New Zealand, and North American datasets have most taxa on the species-level while the Australian dataset has a similar number of taxa on species and genus-level.

\begin{table}[ht]
    \centering
    \caption{Number of taxa per harmonized dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percentage.} 
    \label{tab:tax_coverage}
    \begin{tabular}{lccccc}
    \toprule[.1em]
    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic insects \\ 
    \toprule[.1em]
    EU & 4496 & 3691 (82) & 647 (14) & 158 (4) & 3838 (85) \\ 
    NOA & 3753 & 2414 (64) & 1163 (31) & 176 (5) & 3305 (88) \\ 
    AUS & 1402 & 564 (40) & 578 (41) & 260 (19) & 1016 (72) \\ 
    NZ & 478 & 404 (85) & 47 (10) & 27 (6) & 443 (93) \\ 
    \bottomrule
    \end{tabular}
\end{table}

@@

The amount of entries with available information for the selected grouping features varied strongly for the preprocessed European, North American, and Australian datasets (Table \ref{tab:trait_coverage}). By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).

\begin{table}[ht]
    \centering
    \caption{Rounded percentage of entries that have 
    information for the individual grouping features
    shown per trait dataset.}
    \label{tab:trait_coverage}
    \begin{tabular}{lccccccc}
    \toprule[.1em]
    Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
    \toprule[.1em]
    EU & 8 & 15 & 21 & 36 & 10 & 49 & 75 \\ 
    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
    \bottomrule
    \end{tabular}
\end{table}

### 2020-10-16 Paper/Trait_def_table/Trait_definitions_table.tex
16.10: Paper Update, first implm. of Co-Authors

Definitions of grouping features and traits varied in their level of detail. The Freshwaterecology database, and databases from Tachet and Twardochleb et al. provided more detailed descriptions of their trait information compared to the databases from Vieira et al. and New Zealand. An exception is the Australian trait database which is a collection of seven trait datasets \cite{kefford_integrated_2020}. Thus, grouping features occur multiple times with varying differentiation into traits. Depending on the dataset trait information is described with more or less detail.

The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope. We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}). Both, differences in differentiation and scope can lead to discrepancies in trait definitions. For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways. Tachet defines predators as carvers, engulfers and swallowers. By contrast, in the North American (Twardochleb) database predators are defined as engulfers and carnivorous piercers. In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers. Furthermore, the scope in the Freshwaterecology database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition. Therefore, the Freshwaterecology database defines e.g. predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition. The Tachet database captures the food source in an additional grouping feature. Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}). Locomotion definitions differ also in scope between databases. Freshwaterecology and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation, the North American (Vieira) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb) database includes among the way of movement also the location of movement. Similarly, regarding reproduction trait databases differ in their scope. Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the Freshwaterecology and Tachet databases. North America (Vieira) provides information on the oviposition location but not on reproductive behavior. The Australian database report traits for reproductive behavior but also on oviposition site. The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g. water surface, terrestrial), and egg/egg mass (e.g. free, cemented).

Various codings of traits are used throughout the databases (e.g. binary, fuzzy, continuous). The freshwaterecology and Australian use different codings in their databases. Tachet and the New Zealand database use exclusively fuzzy coding. Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}). Binary coding represents a simple approach in which a taxon either expresses a trait or not. Fuzzy coding characterizes the affinity of an organism to exert a certain trait. It is used to account for plasticity in traits, e.g. taking into account that traits can change over the development time of an organism. Usually, fuzzy coded affinities are converted into proportional values. Continuous coding is used for traits like body size.

@@

% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
% Table with diff trait states and coding
\begin{landscape}
    \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
    \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
    \endfirsthead
    \toprule[.1em]
    \label{tab:trait_databases_coding_differentiation}
    Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
    \toprule[.1em]
    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology}} & 
    10 & 
    6 &
    6 & 
    7 & 
    9 & 
    - & 
    - 
    \\
    \cline{2-8} & 
    \specialcell{10 point \\ assignment \\ system} &
    \specialcell{single category \\ assignment \\ system} &
    \specialcell{10 point \\ assignment \\ system} &
    \multicolumn{2}{c |}{\specialcell{presence/absence assignment \\ system}} &
    - & 
    - \\
    \hline
    \hline
    \multirow{2}{*}{Tachet} & 
    7 & 
    3 &
    8 & 
    5 & 
    8 & 
    7 & 
    - 
    \\
    \cline{2-8} &
    \multicolumn{2}{c |}{fuzzy $[0-3]$} &
    fuzzy $[0-5]$ & 
    \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
    -
    \\
    \hline
    \hline
    \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
    6 & 
    3 &
    10 & 
    3 & 
    10 & 
    3 & 
    - 
    \\
    \cline{2-8} &
    \multicolumn{6}{c |}{binary} &
    -
    \\
    \hline
    \hline
    \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
    8 & 
    3 &
    9 & 
    8 & 
    10 & 
    3 & 
    5 
    \\
    \cline{2-8} &
    \multicolumn{7}{c }{binary}
    \\
    \hline
    \hline
    \multirow{2}{*}[-4mm]{Australia} & 
    16 \textsuperscript{\textit{a}} & 
    7 &
    9 & 
    10 &
    13 \textsuperscript{\textit{b}} & 
    9 & 
    4
    \\
    \cline{2-8} & 
    \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
    binary; fuzzy $[0 - 3]$ & 
    \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
    categorical & 
    \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
    fuzzy codes $[0-3]$
    \\
    \hline
    \hline
    \multirow{2}{*}{New Zealand} & 
    6 & 
    3 & 
    4 & 
    4 & 
    4 & 
    5 & 
    4
    \\
    \cline{2-8} & 
    \multicolumn{7}{c }{fuzzy $[0-3]$}
    \\
    \bottomrule
    \end{longtable}
    \begin{minipage}{\linewidth}\small
        \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
        \newline
        \textit{b} Many traits were rather comments than traits in the original database and were not considered.
    \end{minipage}
\end{landscape}

>>>>

Definitions of grouping features and traits varied in their level of detail in the original trait databases. The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database. An exception is the Australian trait database which is a collection of seven specific trait datasets \cite{kefford_integrated_2020}. Thus, grouping features occur multiple times with varying differentiation into traits. Depending on the dataset trait information is described with more or less detail.

The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope. We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}). Both, differences in differentiation and scope can lead to discrepancies in trait definitions. For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways. The Tachet database defines predators as carvers, engulfers and swallowers. By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers. In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers. Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition. Therefore, the freshwaterecology.info database defines e.g. predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition. The Tachet database captures the food source in an additional grouping feature. Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}). Locomotion definitions differ also in scope between databases. Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement. Similarly, regarding the reproduction traits, databases differ in their scope. Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases. North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior. The Australian database report traits for reproductive behavior but also on oviposition site. The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g. water surface, terrestrial), and egg/egg mass (e.g. free, cemented).

Various codings of traits are used throughout the databases (e.g. binary, fuzzy, continuous). The freshwaterecology.info and Australian use different codings in their databases. Tachet and the New Zealand database exclusively use fuzzy coding. Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}). Binary coding represents a simple approach in which a taxon either expresses a trait or not. Fuzzy coding characterizes the affinity of an organism to exert a certain trait. It is used to account for plasticity in traits, e.g. taking into account that traits can change over the development time of an organism. Usually, fuzzy coded affinities are converted into proportional values. Continuous coding is used for traits like body size.
% Last sentences are a bit redundant

@@

% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
% Table with diff trait states and coding
\begin{landscape}
    \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
    \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
    \endfirsthead
    \toprule[.1em]
    \label{tab:trait_databases_coding_differentiation}
    Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
    \toprule[.1em]
    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology.info}} & 
    10 & 
    6 &
    6 & 
    7 & 
    9 & 
    - & 
    - 
    \\
    \cline{2-8} & 
    \specialcell{10 point \\ assignment \\ system} &
    \specialcell{single category \\ assignment \\ system} &
    \specialcell{10 point \\ assignment \\ system} &
    \multicolumn{2}{c |}{\specialcell{binary}} &
    - & 
    - \\
    \hline
    \hline
    \multirow{2}{*}{Tachet} & 
    7 & 
    3 &
    8 & 
    5 & 
    8 & 
    7 & 
    - 
    \\
    \cline{2-8} &
    \multicolumn{2}{c |}{fuzzy $[0-3]$} &
    fuzzy $[0-5]$ & 
    \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
    -
    \\
    \hline
    \hline
    \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
    6 & 
    3 &
    10 & 
    3 & 
    10 & 
    3 & 
    - 
    \\
    \cline{2-8} &
    \multicolumn{6}{c |}{binary} &
    -
    \\
    \hline
    \hline
    \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
    8 & 
    3 &
    9 & 
    8 & 
    10 & 
    3 & 
    5 
    \\
    \cline{2-8} &
    \multicolumn{7}{c }{binary}
    \\
    \hline
    \hline
    \multirow{2}{*}[-4mm]{Australia} & 
    16 \textsuperscript{\textit{a}} & 
    7 &
    9 & 
    10 &
    13 \textsuperscript{\textit{b}} & 
    9 & 
    4
    \\
    \cline{2-8} & 
    \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
    binary; fuzzy $[0 - 3]$ & 
    \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
    categorical & 
    \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
    fuzzy codes $[0-3]$
    \\
    \hline
    \hline
    \multirow{2}{*}{New Zealand} & 
    6 & 
    3 & 
    4 & 
    4 & 
    4 & 
    5 & 
    4
    \\
    \cline{2-8} & 
    \multicolumn{7}{c }{fuzzy $[0-3]$}
    \\
    \bottomrule
    \end{longtable}
    \begin{minipage}{\linewidth}\small
        \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
        \newline
        \textit{b} Many traits were rather comments than traits in the original database and were not considered.
    \end{minipage}
\end{landscape}
